Macro Impacts

### 2016-07-20 Macro Impacts Revised.tex
Some more good stuff.
The Green’s function is contained in the Realistic file.
Test Again

@@

Note that the results in the section "Penetration" in this paper "Hypervelocity penetration..." are for eroding rods -- but macro doesn't erode.  If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e. earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.

%\pagebreak
%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
\end{document}

>>>>

\pagebreak
\section{Numerical Methods}
From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere. Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$.

@@

Note that the results in the section "Penetration" in this paper "Hypervelocity penetration..." are for eroding rods -- but macro doesn't erode.  If we decided to use equation 39 and the resulting equations which partition the energy of the impact into kinetic, elastic and plastic energy terms of the target (i.e. earth or moon), we'd set $u = v$, and $s = 0$ to eliminate the "eroding" effect.
\end{document}

What is the area per year covered by these non-linear zones as a function of macro mass, volume etc (contour plot).
